---
title: "UN Report on Relationship between GDP and Life Expectancy"
author: "Haley Brown"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse) ##contains ggplot package
```

# Introduction

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

# My Plot
```{r gdp_lifeexp_1997}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, color = continent) +
  geom_point() + labs(x = "GDP per capita", y = "Life Expectancy", title = "GDP per capita vs. Life Expectancy")
```

```{r data_summary, include=FALSE}
nCountries <- length(unique(gapminder_1997$country))
```

The number of countries that entered the above analysis was `r nCountries`.

# Syntax Practice
1. R - it's the only one I know
2. _ggplot_
3. ***practicing***
4. [RMarkdown Cheatsheat](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)

